---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(BuzzardsBay)
library(knitr)
knitr::opts_chunk$set(warning = FALSE) 

```

# BuzzardsBay

<!-- badges: start -->
<!-- badges: end -->

The goal of **BuzzardsBay** (R package) is to process and analyze data for the [Continuous Oxygen Monitoring in Buzzards Bay (COMBB) project](https://www.woodwellclimate.org/project/combb/). 

## Installation

You can install **BuzzardsBay** from [GitHub](https://github.com/) with:

```{r install, eval=FALSE}
# install.packages("devtools")
devtools::install_github("UMassCDS/BuzzardsBay")
```

## Usage

Currently the primary function is `qc_deployment()` it reads in calibrated 
data for a deployment and generates files containing merged and flagged copies
of the data.  It assumes [this file structure and naming convention](https://docs.google.com/document/d/1kJttcEXzpNNknGwjkVwdYHw9LzZyjJ-FaX0CrU7H7NU).
In particular it expects data for a deployment to have this path `/BB_Data/<year>/<site>/<year>-<month>-<day>/`  e.g.
`"~/BB_Data/2022/SR4/2022-07-08"`.  It makes no assumption about the path to 
base directory (`"BB_Data"`) itself.  
Within the deployment directory there should be a "Calibration/" sub-directory
with the calibrated HOBOware output (ending in `.csv` and `Details.txt`) for 
both dissolved oxygen and conductivity/salinity.

Once that's in place we can process the calibrated data in the deployment with
the code below.

```{r run, eval = FALSE }
library(BuzzardsBay)
deployment_dir <- ""  # Provide full path here. Don't include `Calibration/`
qc_deployment(deployment_dir)


```

## Running on example data

Create an example data folder structure and deployment with `setup_example_dir()`. 
If you specify a path with the `parent_dir` argument the example will be created 
there. Otherwise, as in the example below, it creates the example files within
the location specified by `tempdir()`. 
```{r run_example, echo = TRUE, results = "hide"}
paths <- setup_example_dir()  
print(paths)
```

With that in place we can then call `qc_deployment()` on the example 
deployment stored in `paths$deployment` which will also be where the output
files are created.

```{r qc_deployment, echo = TRUE, results = "hide"}
a <- qc_deployment(paths$deployment)

```
The code above will only work once as `qc_deployment()` will throw an error if
the output already exists. To run again delete all the example data in 
`paths$base`.

### Output

`qc_deployment()` writes two identical CSV files and a metadata file to the
deployment directory. 

* `Auto_QC_<deployment>.csv` is a permanent record of this state of the process 
and should not be edited.
*  `Preliminary_QC_<deployment>.csv` is for subsequent review and editing. 
`Preliminary_` should be dropped from the name when review is complete.
* `Metadata_<deployment>.yml` contains the metadata written as a YAML file.

#### Tabular data 

Here are a few lines of the data written to the two CSV files when using 
`setup_example_dir()`.

```{r table, echo = FALSE}
  options(knitr.kable.NA = '')
  knitr::kable(a$d[41:50, ], row.names = FALSE, format.args = ) 


```

#### Metadata

This is the metadata derived from the example.

```{r md, results = "asis", echo = FALSE}
cat(faux::nested_list(a$md))
```




