---
title: "Setting up and using example data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


Example data files are included with the **BuzzardsBay** package 
to facilitate code development and testing.
You can also use this example data to play with the package functions
independent of a pre-existing or important data archive.

## Setup
Load the package:

```{r setup}
library(BuzzardsBay)
```

## All the example files

To put all the example data in the package in one large example data store
with many files:
```{r example dir}
paths <- setup_example_dir()
```
by default it will be set up in a path created by `tempdir()` but you can
also use the `parent_dir` argument to specify where you want it created.

## A subset of example files

You can  use combinations of the filter arguments to specify a subset
of the data you want to include in the example data store. This will be 
quicker and use less disk space than including all the files.

For example to get a single deployment:

```{r, eval = FALSE}
paths <- setup_example_dir(site_filter =  "RB1",
                           deployment_filter = "2023-06-09")
print(paths$deployments)
qc_deployment(paths$deployments[1])
```

Or to get all the deployments for site WH1X:

```{r, eval = FALSE}
paths <- setup_example_dir(site_filter =  "WH1X", delete_old = TRUE)
print(paths$deployments)
```

`delete_old = TRUE` was added to clear out the prior example data and is useful
if you want to reset the example - perhaps clearing out previously run reports
and QC files.

--------------------------------------------------------------------------------

# Available example datasets 

These are grouped into examples for the analysis module and the qc module. The
formats of the two sets of files is different so each example deployment will
only work for one of the two sets of functions.

```{r echo=FALSE, results='asis'}
# This inserts the README in extdtata into the vignette output
# (Describing all the datasets)
cat(readLines(system.file(package = "BuzzardsBay", "extdata/README.md"))[-1],
    sep = "\n")
```
