---
output: html_document
params:
  paths: NULL
---

```{r setup, include=FALSE}
library(BuzzardsBay)
library(readr)
library(dplyr)
library(ggplot2)
library(knitr)
library(plotly)
knitr::opts_chunk$set(echo = FALSE, out.width = "100%")
```


```{r preprocess data, include=FALSE}

paths <- params$paths

data_path <-  paths$deployment_auto_qc
sites_path <- paths$sites
metadata_path <- paths$deployment_metadata
preceding_auto_qc <- paths$preceding_auto_qc

using_example_data <- FALSE


# If all parameters are null substitute paths to example files
# (for testing and debugging)
n_null <- sum(is.null(data_path), is.null(sites_path),
              is.null(metadata_path), is.null(preceding_auto_qc))
if (! n_null %in% c(0, 4))
  stop("Either all required paths should be set or none (to use example files)")
if (n_null == 4) {
  message("Running with example files from package.")

  paths <- list()

  paths$data_path <- system.file("extdata/qc_example.csv",
                                 package = "BuzzardsBay",
                                 mustWork = TRUE)
  paths$sites_path <- system.file("extdata/sites.csv",
                                  package = "BuzzardsBay",
                                  mustWork = TRUE)
  paths$metadata_path <- system.file("extdata/qc_example.yml",
                                     package = "BuzzardsBay",
                                     mustWork = TRUE)
  paths$global_parameters <- system.file("extdata/bb_parameters.yml",
                                         package = "BuzzardsBay",
                                         mustWork = TRUE)

  paths$preceding_auto_qc <- NA
  paths$site_parameters <- NA
  using_example_data <- TRUE
}


update_bb_parameters(paths)

has_preceding_data <- "preceding_auto_qc" %in% names(paths) &&
  !is.na(paths$preceding_auto_qc)

# Read data
d <- readr::read_csv(data_path, col_types = readr::cols())
sites <- readr::read_csv(sites_path, col_types = readr::cols())
md <- yaml::read_yaml(metadata_path)
d$Date_Time <- format_csv_date_time(d$Date_Time)

# Convert sites to list with just current site
site <- md$site
n_match <- sum(sites$site == site)
if (n_match != 1)
  stop("Expected one and only one site in ", sites_path, " 
       to match the current site (", site, ") but found ", n_match)

if (!site == d$Site[1])
  stop("Metadata site (", site, ") does not match data site (", d$Site[1], ")")

sites <- sites[sites$site == site, , drop = FALSE] |> as.list()

# Add daylight info to d

d$daylight <- is_daylight(d$Date_Time,
                          lat = sites$latitude,
                          lon = sites$longitude,
                          tz = md$timezone)


d$Prior_Dep <- FALSE

prior_deployment_desc_text <- ""
if (has_preceding_data) {
  pd <- readr::read_csv(paths$preceding_auto_qc, show_col_types = FALSE)
  pd$Date_Time <- format_csv_date_time(pd$Date_Time)

  inclusion_lag <- lubridate::make_difftime(6 * 60^2) # 6 hours
  start <- min(lubridate::as_datetime(d$Date_Time), na.rm = TRUE)

  dt <- lubridate::as_datetime(pd$Date_Time)
  sv <- dt > (start - inclusion_lag) & dt < start
  if (sum(sv) == 0) {
    has_preceding_data <- FALSE
  } else {
    pd <- pd[sv, , drop = FALSE]
    pd$daylight <-  is_daylight(pd$Date_Time,
                                lat = sites$latitude,
                                lon = sites$longitude,
                                tz = md$timezone)
    pd$Prior_Dep <- TRUE

    d <- rbind(pd, d)
  }
  prior_deployment_desc_text <-
    paste0("Red circles surround the location of the last observation in the ",
           "prior deployment and the first observation in the current ",
           "deployment.")
}


# Reformat to long (dl is for data, long)
data_cols <- c("Temp_DOLog",
               "Temp_CondLog",
               "Raw_DO",
               "DO",
               "DO_Pct_Sat",
               "Salinity",
               "High_Range",
               "Spec_Cond")
id_cols <- c("Site", "Date", "Date_Time", "Gen_QC", "Flags", "Prior_Dep")

dl <- select(d, all_of(c(id_cols, data_cols))) |>
  tidyr::pivot_longer(cols = all_of(data_cols))

# Aggregate parameters

# With real data, update parameter based on global and site parameters
if (!using_example_data) {
  # The example data files for the markdown report are not nested in
  # a file hierarchy, so the parameter files aren't in the right relative
  # locations.
  update_bb_parameters(paths =
                         lookup_paths(deployment_dir = dirname(data_path)))
}
# Make local copy of parameters
# Necessary because bbp isn't exported from package and I like the shorthand
# way of referencing it
bbp <- bb_options()


# Record counts
n_ir <- sum(d$Gen_QC == 9 & !d$Prior_Dep, na.rm = TRUE) # immediate rejection
n_to_review <- sum(d$Gen_QC == 9999 & !d$Prior_Dep, na.rm = TRUE)

has_salinity_data <- !all(is.na(d$Salinity))

# Generate text to describe calibration ratios if they exist and aren't NA
has_ratios <-
  all(c("start_ratio", "end_ratio") %in% names(md$do_calibration)) &&
  all(!is.na(md$do_calibration[c("start_ratio", "end_ratio")]))
# nolint start: indentation_linter
calibration_text <- ifelse(
  has_ratios,
  paste0("DO calibration ratios (start, end): ",
         round(md$do_calibration$start_ratio, 3), ", ",
         round(md$do_calibration$end_ratio, 3), "\n"),
  "")
# nolint end

```

---
title: "`r site`, `r md$deployment_date`"
---
## Quality assessment report
### [Continuous Oxygen Monitoring in Buzzards Bay (COMBB) project](https://www.woodwellclimate.org/project/combb/)

________________________________________________________________________________

## Deployment info

Report date: `r lubridate::today()`  
Site: `r md$site`  
Deployment: `r md$deployment_date`  
Records: `r nrow(d)`  
Calibration start: `r md$calibration_start`
Calibration end : `r md$calibration_end`  
Percent calibrated: `r round(md$pct_calibrated, 2)`  
Percent (and number) immediate rejection: `r md$pct_immediate_rejection`
(`r n_ir`)  
Percent (and number) flagged for review: `r md$pct_flagged_for_review`
(`r n_to_review`)  
`r calibration_text`
Input path: `r data_path`  

## Dissolved Oxygen

### Raw and calibrated dissolved oxygen (mg/l)

Vertical rectangles indicate flags, red for dissolved oxygen (DO),
orange for other flags.  
Thresholds are shown as horizontal lines if they are exceeded by the data.  
Dots mark both ends of jumps that are greater than `r bbp$do_max_jump`.  
`r prior_deployment_desc_text`

```{r DO static plot, echo=FALSE, message=TRUE, warning=TRUE}


# Loggical indicating sensor error value was detected
p <- bb_plot(d,
             dl,
             focal_columns = c("DO", "Raw_DO"),
             jump_pattern = "[:^]Dj|Rj",
             focal_flag_pattern = "[:^]D|R",
             err_pattern = "De",
             plot_label = "Dissolved Oxygen",
             focal_flag_label = "DO",
             y_label = "Dissolved Oxygen (mg/l)",
             threshold_values = c(bbp$max_raw_do,
                                  sites$Max_QC_Raw_DO,
                                  sites$Max_QC_DO,
                                  sites$Min_QC_Raw_DO,
                                  sites$Min_QC_DO),
             threshold_labels = c("Max Raw DO (Immediate Rejection)",
                                  "Max Site Raw DO (Rsh)",
                                  "Max Site DO (Dsh)",
                                  "Min Site Raw DO (Rsl)",
                                  "Min Site DO (Dsl)"),
             threshold_colors = rgb(1, 0, 0, .8),
             range_limit = c(bb_options("plot_min_do"),
                             bb_options("plot_max_do")))


suppress_specific_warnings(print(p))


```


### Calibrated dissolved oxygen (mg/l), interactive plot

Vertical rectangles indicate flags, red for dissolved oxygen orange for other
flags.  
Dashed horizontal lines are plotted for site specific thresholds but 
may not be visible until the plot is zoomed out.  


```{r DO interactive plot}

bb_interactive_plot(d, dl,
                    focal_column = c("DO"),
                    jump_pattern = "[:^]Dj",
                    focal_flag_pattern = "[:^]D",
                    plot_label = "Dissolved Oxygen",
                    focal_flag_label = "DO",
                    y_label = "Dissolved Oxygen (mg/l)",
                    threshold_values = c(sites$Max_QC_DO,
                                         sites$Min_QC_DO),
                    threshold_labels = c("Max Site DO (Dsh)",
                                         "Min Site DO (Dsl)"),
                    threshold_colors = c("purple", "purple"),
                    range_limit = c(bb_options("plot_min_do"),
                                    bb_options("plot_max_do")))



```


## Salinity


`r ifelse(has_salinity_data, "", "There is no salinity data to plot.")`

```{r salinity static plot,  eval = has_salinity_data}

asis_output("### Calibrated salinity (ppt)")

p <- bb_plot(d, dl,
             focal_column = "Salinity",
             jump_pattern = "Sj",
             focal_flag_pattern = "S",
             err_pattern = "Se",
             plot_label = "Salinity",
             y_label = "Salinity (ppt)",
             threshold_values = c(sites$Max_QC_Sal, sites$Min_QC_Sal),
             threshold_labels = c("Max Site Salinity (Ssh)",
                                  "Min Site Salinity (Ssl)"),
             threshold_colors = rgb(1, 0, 0, .8),
             range_limit = c(bb_options("plot_min_sal"),
                             bb_options("plot_max_sal")))
suppress_specific_warnings(print(p))

```

```{r salinity interactive plot, eval = has_salinity_data}
asis_output("### Calibrated salinity (ppt), interactive plot")

bb_interactive_plot(d, dl,
                    focal_column = "Salinity",
                    jump_pattern = "Sj",
                    focal_flag_pattern = "S",
                    plot_label = "Salinity",
                    y_label = "Salinity (ppt)",
                    threshold_values = c(sites$Max_QC_Sal, sites$Min_QC_Sal),
                    threshold_labels = c("Max Site Salinity (Ssh)",
                                         "Min Site Salinity (Ssl)"),
                    threshold_colors = c("purple", "purple"),
                    range_limit = c(bb_options("plot_min_sal"),
                                    bb_options("plot_max_sal")))


```



## Temperature

### Temperature from Conductivity and DO loggers (Deg. C)

```{r temp static plot}


p <- bb_plot(d, dl,
             focal_column = c("Temp_DOLog", "Temp_CondLog"),
             jump_pattern = "TDj|TCj",
             focal_flag_pattern = "TD|RC",
             err_pattern = "TDe|RCe",
             plot_label = "Temperature",
             y_label = "Temperature (C)",
             threshold_values = c(sites$Max_QC_Temp,
                                  sites$Min_QC_Temp,
                                  bbp$max_temp,
                                  bbp$min_temp),
             threshold_labels = c("Max Site Temp (TDsh, TCsh)",
                                  "Min Site Temp (TDsl, TCsl)",
                                  "Max Temp (TDh, TCh)",
                                  "Min Temp (TDl, TCl)"),
             threshold_colors = rgb(1, 0, 0, .8),
             range_limit = c(bb_options("plot_min_temp"),
                             bb_options("plot_max_temp")))

suppress_specific_warnings(print(p))

```

### Temperature from DO logger (Deg C.), interactive plot

```{r temp interactive plot}

bb_interactive_plot(d, dl,
                    focal_column = c("Temp_DOLog"),
                    jump_pattern = "TDj|TCj",
                    focal_flag_pattern = "TD|RC",
                    plot_label = "Temperature",
                    y_label = "Temperature (C)",
                    threshold_values = c(sites$Max_QC_Temp,
                                         sites$Min_QC_Temp,
                                         bbp$max_temp,
                                         bbp$min_temp),
                    threshold_labels = c("Max Site Temp (TDsh, TCsh)",
                                         "Min Site Temp (TDsl, TCsl)",
                                         "Max Temp (TDh, TCh)",
                                         "Min Temp (TDl, TCl)"),
                    threshold_colors = c("purple", "purple", "red", "red"),
                    range_limit = c(bb_options("plot_min_temp"),
                                    bb_options("plot_max_temp")))
```
