---
header-includes:
   - \usepackage[default]{sourcesanspro}
   - \usepackage[T1]{fontenc}
   - \usepackage[margins=raggedright]{floatrow} 
   - \usepackage{fancyhdr}
   - \pagestyle{fancy}
   - \fancyhf{}
   - \renewcommand{\headrulewidth}{0pt}
   - \fancyfoot[C]{\thepage}
   - \usepackage{floatrow}
   - \floatsetup[figure]{capposition=top}
output: 
   pdf_document
documentclass: report
pagestyle: empty
geometry: 
- margin=1in
- top=0.5in
- bottom=0.75in
fontsize: 12pt 
urlcolor: blue
params:
  title: ''
  date: ''
  stat: ''
  value: ''
  plots: ''
---

```{r include = FALSE}
knitr::opts_chunk$set(dev="pdf")
```

## `r params$title`

Continuous Oxygen Monitoring in Buzzards Bay (COMBB)

Seasonal report, `r params$date`


### Seasonal statistics

**Statistic** | **Value** |
---|---:
`r params$stat[1]` | `r params$value[1]`
`r params$stat[2]` | `r params$value[2]`
`r params$stat[3]` | `r params$value[3]`
`r params$stat[4]` | `r params$value[4]`
`r params$stat[5]` | `r params$value[5]`
`r params$stat[6]` | `r params$value[6]`
`r params$stat[7]` | `r params$value[7]`
`r params$stat[8]` | `r params$value[8]`
`r params$stat[9]` | `r params$value[9]`
`r params$stat[10]` | `r params$value[10]`
`r params$stat[11]` | `r params$value[11]`
`r params$stat[12]` | `r params$value[12]`
`r params$stat[13]` | `r params$value[13]`
`r params$stat[14]` | `r params$value[14]`
`r params$stat[15]` | `r params$value[15]`
`r params$stat[16]` | `r params$value[16]`
`r params$stat[17]` | `r params$value[17]`
`r params$stat[18]` | `r params$value[18]`
`r params$stat[19]` | `r params$value[19]`
`r params$stat[20]` | `r params$value[20]`
`r params$stat[21]` | `r params$value[21]`
`r params$stat[22]` | `r params$value[22]`
`r params$stat[23]` | `r params$value[23]`
`r params$stat[24]` | `r params$value[24]`
`r params$stat[25]` | `r params$value[25]`
`r params$stat[26]` | `r params$value[26]`
`r params$stat[27]` | `r params$value[27]`
`r params$stat[28]` | `r params$value[28]`

*Only days that fall below the threshold are counted in mean durations.


<!-- do_pct_sat -->
```{r echo = FALSE, warning = FALSE, fig.cap = plot_info['do_pct_sat', 'caption']}
plot <- plot_info['do_pct_sat', ]
make_plot(core, y = core$DO_Pct_Sat, x_lab = plot$x_label, y_lab = plot$y_label)
```

<!-- do -->
```{r echo = FALSE, warning = FALSE, fig.cap = plot_info['do', 'caption']}
plot <- plot_info['do', ]
make_plot(core, y = core$DO, x_lab = plot$x_label, y_lab = plot$y_label, hline = 6)
```

<!-- do_daily_range -->
```{r echo = FALSE, warning = FALSE, fig.cap = plot_info['do_daily_range', 'caption']}
plot <- plot_info['do_daily_range', ]
make_plot(daily, x = daily$Date, y = daily$DO_range, x_lab = plot$x_label, y_lab = plot$y_label, point_size = 1)
```

<!-- do_daily_min -->
```{r echo = FALSE, warning = FALSE, fig.cap = plot_info['do_daily_min', 'caption']}
plot <- plot_info['do_daily_min', ]
make_plot(daily, x = daily$Date, y = daily$DO_min, x_lab = plot$x_label, y_lab = plot$y_label, point_size = 1)
```


<!-- pair_mean_do_temp -->
```{r echo = FALSE, warning = FALSE, fig.cap = plot_info['pair_mean_do_temp', 'caption']}
plot <- plot_info['pair_mean_do_temp', ]
make_facet_plot(daily)
```

<!-- daily_pct_under_6 -->
```{r echo = FALSE, warning = FALSE, fig.cap = plot_info['daily_pct_under_6', 'caption']}
plot <- plot_info['daily_pct_under_6', ]
make_plot(daily, x = daily$Date, y = daily$DO_6_pct, x_lab = plot$x_label, y_lab = plot$y_label, point_size = 1)
```

<!-- rolling_7_day_do -->
```{r echo = FALSE, warning = FALSE, fig.cap = plot_info['rolling_7_day_do', 'caption']}
plot <- plot_info['rolling_7_day_do', ]
make_plot(core, x = core$Date_Time, y = core$rolling_do, x_lab = plot$x_label, y_lab = plot$y_label, point_size = 0, linetype = 1, hline = 6)
```

<!-- daily_temp -->
```{r echo = FALSE, warning = FALSE, fig.cap = plot_info['daily_temp', 'caption']}
plot <- plot_info['daily_temp', ]
make_plot(core, y = core$Temp_CondLog, x_lab = plot$x_label, y_lab = plot$y_label)
```

<!-- daily_salinity -->
```{r echo = FALSE, warning = FALSE, fig.cap = plot_info['daily_salinity', 'caption']}
plot <- plot_info['daily_salinity', ]
make_plot(daily, x = daily$Date, y = daily$salinity, x_lab = plot$x_label, y_lab = plot$y_label, point_size = 1)
```

<!-- do_bw -->
```{r echo = FALSE, warning = FALSE, fig.cap = plot_info['do_bw', 'caption']}
if(baywatchers) {
   plot <- plot_info['do_bw', ]
   make_plot_2var(core, bay, x1 = core$Date_Time, y1 = core$DO, x2 = bay$Date_Time, y2 = bay$DO, x_lab = plot$x_label, y_lab = plot$y_label)
}
```

<!-- scat_bw_sensor -->
```{r echo = FALSE, warning = FALSE, fig.cap = plot_info['scat_bw_sensor', 'caption']}
if(baywatchers) {
   plot <- plot_info['scat_bw_sensor', ]
   make_plot(bay, x = bay$DO, y = bay$Sensor_DO, x_lab = plot$x_label, y_lab = plot$y_label, diag = TRUE, point_size = 1)
}
```
